---
title: "glm_analysis"
format:
  pdf:
    keep-tex: false
    pdf-engine: pdflatex
    include-in-header:
      text: |
        \usepackage{natbib}
        \usepackage{pdflscape}
        \usepackage{caption}
        \captionsetup{format=plain, labelsep=period, justification=justified, singlelinecheck=false, indention=0pt}
  latex:
    fig-format: png
    fig-dpi: 300
  docx:
    fig-dpi: 300
    reference-doc: reference.docx
execute:
  dir: project
editor:
  markdown:
    wrap: 72
---

```{r setupQuarto, echo=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)

if (knitr::pandoc_to("docx")) {
  dev_docx <- if (requireNamespace("ragg", quietly = TRUE)) "ragg_png" else "png"
  knitr::opts_chunk$set(
    dev = dev_docx,
    dpi = 300,
    fig.retina = 1
  )
}
```

```{r loadResults, include=FALSE}
# Load pre-computed and formatted results.
# To regenerate: run 2_fit_models.R then 3_format_results.R from the project root.
library(tidyverse)
library(scales)
library(ggtext)
source("functions/format_numeric_cols.R")

load("scripts/intermediate_outputs/formatted_results.RData")

# Display name lookups (artLabels, natcanLabels, natcanImgLabels, artImgLabels)
# -- shared with the plotting functions built in 3_format_results.R, so this
# is sourced rather than defined here directly.
source("scripts/plotting/plot_label_lookups.R")


```

Evidence that wasps can use overhead patterns to navigate comes from two
observations. First, that the proportion of choices for the rewarding
pattern $P_{\mathrm{corr}}$ is \>50% and second, that this proportion
drops when the patterns are removed from the ceiling (during the
control). We begin by asking whether wasps can discriminate stimulus
patterns consisting of black stripes oriented perpendicularly to each
other on the first-chamber ceilings of the two Y-maze arms (for stimulus
conditions, see Figure 2A).

## Can wasps discriminate 'simple' artificial dorsal patterns?

For the test phase of the perpendicular-parallel artificial stimulus
pair, trial number had a significant positive effect on
$P_{\mathrm{corr}}$ ([@fig-q2]A, solid line;
p`r mAllCoefsRef["perpPara_170725", "rank_trial_pFmt"]`), with
$P_{\mathrm{corr}}$ rising from
`r emmPtsRef["perpPara_170725", "first_prob"]`% (95% CI
`r emmPtsRef["perpPara_170725", "first_confint"]`) at trial 1 to
`r emmPtsRef["perpPara_170725", "last_test_prob"]`% (95% CI
`r emmPtsRef["perpPara_170725", "last_test_confint"]`) by test end, at
trial `r emmPtsRef["perpPara_170725", "last_test_rank_trial"]`
(@tbl-overview), which was significantly above chance (lower 95% CI
bound \>50%; @fig-q2 test panel).

Additionally a Wald z-test revealed end-of-test $P_{\mathrm{corr}}$ was
significantly higher than at the start of the control phase
(`r emmPtsRef["perpPara_170725", "ctrl_start_prob"]`%, 95% CI
`r emmPtsRef["perpPara_170725", "ctrl_start_confint"]`; [@fig-q2]A), with an
odds ratio of `r contrastsRef["perpPara_170725", "odds.ratio"]`
(p`r contrastsRef["perpPara_170725", "pFmt"]`; @tbl-overview).

Also note that $P_{\mathrm{corr}}$ is significantly above chance from an
early trial number (grey shaded 95% confidence ribbon in [@fig-q2]A does
not overlap the 50% line) and remains that way until the end of the
test. In contrast, the $P_{\mathrm{corr}}$ in the control phase is never
significantly above chance for the duration of the control (95%
confidence ribbon overlaps the 50% line), as one would expect for wasps
making choices in the absence of any information regarding the location
of the reward.

<!-- I've removed below paragraph because honestly I'm not sure what the reason
for an elevated prediction at trial 1 could be.

That the model suggests naive wasps nearly perform significantly above
chance at the onset of the test phase (ie. in trial 1) is possibly due
to the model being unable to fit the rapid learning of the wasps, rather
than to the wasps having learned olfactory / temporal cues during the
pre-test training phase that persisted into the test. This is supported
by the proportion of correct decisions in the first few 3-trial wide
windows of the test phase (grey points, [@fig-q2]A) that are clustered
around 50%. -->

## What information are wasps using to discriminate patterns?

```{r fig-q2}
#| fig-cap: 'Wasp reward-navigation performance for artificial stimulus experiments. Each row shows one experiment with a particular pair of stimuli (stimulus conditions as in Figure 2A-D); columns show test and, when run, control phases per experiment. During the test phase, overhead artificial stimuli could be used by the wasps to choose the rewarding chamber, but during the control phase, when these stimuli were removed, performance dropped to chance levels. The y-axis represents $P_{\mathrm{corr}}$, the probability of a wasp entering (or "choosing") the second arm chamber that contained the reward (constituting a "correct choice"). The solid black line shows the predicted probability of correct choices across trials and the grey ribbon the 95% confidence interval around these probabilities given by the models. Grey points are the proportion (not the probability) of correct choices made by all wasps in 3-trial wide rolling windows. Points represent the predicted probabilities of correct choices at the end of the test and the start of the control phases, and the error bars the 95% confidence intervals around these predictions. For the perpendicular/parallel pair the end-of-test point (trial 47) is drawn as an open circle and repeated on the thin-oblique test panel, so that the two pairs can be compared at the same trial `(Eq.~\ref{eq:martcompare})`{=latex}. The dashed horizontal line represents chance performance (50%). Only the first choice of each wasp in each trial was used as data in the model and to calculate the rolling means.'
#| fig-height: 4.6

print(fig_q2)
```

```{r q2ContrastArtStimuli}
q2TrialSlopeTable <- allTrialSlopeRef %>%
  filter(nat_or_art == "artificial") %>%
  select(-nat_or_art)

```

In the previous experiment ([@fig-q2]A), wasps may have located the
rewarding arm using front-to-back optic flow differences:
parallel stripes generate little optic flow for a wasp flying along
them, whereas perpendicular stripes generate a great deal. To test this,
we next used oblique stripes oriented 45° to the right or left of the
Y-maze arm’s long axis (for stimulus conditions, see Figure 2B,C).
Because local motion detectors respond to the component of
optic flow perpendicular to an edge or contour
`\citep{Borst1993}`{=latex}, these two patterns generate an equal
front-to-back optic flow component, differing only in the direction of
their left--right component (a consequence of the aperture problem). If
wasps rely on front-to-back optic flow, they should discriminate the oblique
pair poorly, or at least less well than the perpendicular-parallel pair.

Wasps had no trouble distinguishing between oblique stripes that produce
similar rates of front to back optic flow in the dorsal visual field
([@fig-q2]B, C). For the thin oblique stripe condition
(Figure 2B; [@fig-q2]B), trial had a significant positive effect on
$P_{\mathrm{corr}}$ (p`r q2TrialSlopeTable["thinOb_150823", "pFmt"]`;
@tbl-model-coefs), with performance rising from
`r emmPtsRef["thinOb_150823", "first_prob"]`% (95% CI
`r emmPtsRef["thinOb_150823", "first_confint"]`) at trial 1 to
`r emmPtsRef["thinOb_150823", "last_test_prob"]`% (95% CI
`r emmPtsRef["thinOb_150823", "last_test_confint"]`) by test end, at
trial `r emmPtsRef["thinOb_150823", "last_test_rank_trial"]` ---
significantly above chance (50%). $P_{\mathrm{corr}}$ at test end was
also significantly above performance at the start of the control phase
(`r emmPtsRef["thinOb_150823", "ctrl_start_prob"]`%, 95% CI
`r emmPtsRef["thinOb_150823", "ctrl_start_confint"]`), with an odds ratio
of `r contrastsRef["thinOb_150823", "odds.ratio"]`
(p`r contrastsRef["thinOb_150823","pFmt"]`; @tbl-overview). Again, the
$P_{\mathrm{corr}}$ in the control phase was never significantly above
chance for the duration of the control (95% confidence ribbon overlaps
the 50% line),

For the thick oblique experiment (Figure 2C; [@fig-q2]C), trial had a positive but
non-significant effect on $P_{\mathrm{corr}}$ (p =
`r q2TrialSlopeTable["thickOb_140823", "pFmt"]`; @tbl-model-coefs), with
performance rising from `r emmPtsRef["thickOb_140823", "first_prob"]`%
to `r emmPtsRef["thickOb_140823", "last_test_prob"]`% by test end, at
trial `r emmPtsRef["thickOb_140823", "last_test_rank_trial"]` ---
also significantly above chance. Taken together, the above results show that at least front to back optic flow is not necessary for pattern discrimination.

Performance also differed between stimulus types: at the same trial-point
in both experiments (trial 47; [@fig-q2]A, B, open points), $P_{\mathrm{corr}}$ was
`r artCompareGrp["perpPara_170725", "prob"]`% (95% CI
`r artCompareGrp["perpPara_170725", "confint"]`) for the
perpendicular/parallel pair and
`r artCompareGrp["thinOb_150823", "prob"]`%
(`r artCompareGrp["thinOb_150823", "confint"]`) for the thin oblique
pair (odds ratio `r artCompareRef$oddsRatio`, 95% CI
`r artCompareRef$confint`, p = `r artCompareRef$pFmt`;
Table `\ref{tbl-cross-coefs}`{=latex}), indicating that
discrimination is not equally easy for all artificial patterns tested.
Since the perpendicular-parallel pair presents a stronger combined optic
flow contrast than the thin oblique pair, this suggests that optic
flow contrast may contribute to pattern discrimination. However, since
each stimulus type is represented by a single experiment, we cannot rule
out that this difference is due to variation at the level of the
experiment (e.g., wasp cohort, testing day, or season) rather than the
stimulus pair itself. Side biases were substantial in these two experiments and ran in
opposite directions: with the perpendicular-parallel pair wasps chose
correctly on `r sideBiasRef["perpPara_170725", "L"]`% of left-reward and
`r sideBiasRef["perpPara_170725", "R"]`% of right-reward trials, whereas
with the thin oblique pair the figures were
`r sideBiasRef["thinOb_150823", "L"]`% and
`r sideBiasRef["thinOb_150823", "R"]`% (raw test-phase proportions; model
estimates in @tbl-model-coefs). Reward side is therefore included in
every model and, in the joint model, allowed to differ between
experiments `(Eq.~\ref{eq:martcompare})`{=latex}.

Next, we asked whether wasps could discriminate between an opaque and
transparent ceiling, i.e. between stimuli that lacked
pattern information but presented clear differences in brightness (stimulus
condition as in Figure 2D; [@fig-q2]D). Trial had a positive but non-significant
effect on $P_{\mathrm{corr}}$ (p =
`r q2TrialSlopeTable["brightDiff_250725", "pFmt"]`; @tbl-model-coefs),
likely due to the shorter number of trials run in this experiment, and
performance rose from `r emmPtsRef["brightDiff_250725", "first_prob"]`%
(95% CI `r emmPtsRef["brightDiff_250725", "first_confint"]`) at trial 1
to `r emmPtsRef["brightDiff_250725", "last_test_prob"]`% (95% CI
`r emmPtsRef["brightDiff_250725", "last_test_confint"]`) by test end, at
trial `r emmPtsRef["brightDiff_250725", "last_test_rank_trial"]`.
While performance at the end of the experiment is only borderline
significantly higher than 50%, this is likely an artefact of the
increased uncertainty in the slope / effect of trial number on
performance due to the lower number of trials run in this experiment. If
one for example looks at the middle trials (@tbl-overview), the lower
bound of performance is considerably higher than chance.

## Can wasps use naturalistic patterns for navigation?

```{r fig-q3-tc}
#| fig-cap: 'Wasp reward-navigation performance for six naturalistic forest canopy stimuli. Each row shows wasp performance over two phases (columns: test and control) of each experiment. In the test phase, a pair of naturalistic stimuli (at right) were displayed dorsally in a Y-maze, with one of the stimuli in the pair associated with a reward and the other with no reward (see Methods for further details). During the control phase the stimuli were removed but the reward remained in place. Not all experiments had a control phase (blank panels). Note that performance is only significantly above chance for some stimulus pairs / experiments, and that predicted performance at the end of the test is rarely significantly higher than at the start of the control. All other figure conventions as in Figure 3.'
#| fig-height: 5
#| fig-pos: "p"

print(fig_q3_tc)
```

Evidence for whether wasps can discriminate naturalistic canopies (see
Figure 2E--J) at above-chance rates (\>50%) is mixed. In three of the
six naturalistic canopy pairs we tested, the predicted
$P_{\mathrm{corr}}$ by the end of the test was significantly (canopy E,
G) or borderline significantly (canopy I) above chance (the lower limit
of the 95% CI is \>50%; [@fig-q3-tc]A, C, E, @tbl-overview, @fig-supp-canopyG1),
but for the other three canopy pairs ([@fig-q3-tc]B, D, F) this was not the case. This
suggests that wasps may be able to separate certain pairs of
naturalistic canopies, although the performance is generally lower than
for artificial stimuli (see below).

Three of the naturalistic canopies showed a $P_{\mathrm{corr}}$
significantly or near-significantly greater than 50%. For two of these ([@fig-q3-tc]A, C),
we also ran a control (patterns removed) immediately after the test
phase concluded, but only for Canopy G was the $P_{\mathrm{corr}}$ at
the end of the test significantly higher than at the start of the
control. This is likely due to two factors: $P_{\mathrm{corr}}$ for
naturalistic canopies is generally only modestly above 50% to begin with
(if at all), and the control phases were run for relatively few trials,
which increases the uncertainty in the estimated $P_{\mathrm{corr}}$ at
the start of the control.

## Performance differences among naturalistic and artificial stimuli

Discrimination performance for naturalistic canopies tends to be lower
than for artificial canopies (@fig-q3-combined). The naturalistic canopy
showing the best performance (`r q3NatBest$label`, $P_{\mathrm{corr}}$ =
`r q3NatBest$prob`%) still has a lower $P_{\mathrm{corr}}$ than the
artificial canopy with the worst performance (Transparent/Opaque,
$P_{\mathrm{corr}}$ = `r q3ArtWorst$prob`%; both values at the end of
the test phase). To formally test this, we fitted a GLMM
combining all experiments (test phase only) with stimulus category
(artificial vs. naturalistic) as a fixed effect and experiment identity
as a random effect --- since each category is represented by several
experiments (4 artificial, 7 naturalistic), this separates the category
effect from ordinary experiment-to-experiment variation, with
individuals modelled as nested within experiments. At the maximum
test-phase trial common to all experiments (trial 26),
$P_{\mathrm{corr}}$ was `r natArtCompareGrp["artificial", "prob"]`% (95%
CI `r natArtCompareGrp["artificial", "confint"]`) for artificial stimuli
and `r natArtCompareGrp["naturalistic", "prob"]`%
(`r natArtCompareGrp["naturalistic", "confint"]`) for naturalistic
stimuli (odds ratio `r natArtCompareRef$oddsRatio`, 95% CI
`r natArtCompareRef$confint`, p`r natArtCompareRef$pFmt`;
Table `\ref{tbl-cross-coefs}`{=latex}).

Additionally, the effects of trial on $P_{\mathrm{corr}}$ were modest
for naturalistic stimuli in comparison to artificial stimuli (compare
trial coefficients in @tbl-model-coefs) and were only significantly
greater than zero for canopy G. This translated to small performance
increases between trial 1 and trial 26 for naturalistic stimuli relative
to artificial stimuli (@tbl-overview).

```{r fig-q3-combined}
#| fig-cap: "Probability of correct choices for naturalistic and artificial experiments at the maximum test-phase trial common to all experiments (trial 26). A. Probability of a correct choice across all experiments in the same plot (best fit lines) and 95% confidence intervals around those probabilities (shaded ribbons). Points show the predicted probability of a correct choice at trial 26. B. A comparison of performance at trial 26 for experiments using artificial and naturalistic stimuli. Note: the points in B are the same as those in A."

print(fig_q3_combined)
```

# Supplementary

```{r loadSuppResults}
#| include: false
load("scripts/intermediate_outputs/supp_analysis_results.RData")
```

```{=latex}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
```

```{r supplementaryTbls}
roundNumsInString <- function(x, digits = 2) {
  vapply(
    x,
    function(s) {
      nums <- regmatches(s, gregexpr("-?[0-9]+\\.?[0-9]*", s, perl = TRUE))[[1]]
      if (length(nums) == 0) return(s)
      out     <- s
      rounded <- sprintf(paste0("%.", digits, "f"), as.numeric(nums))
      for (i in seq_along(nums)) out <- sub(nums[i], rounded[i], out, fixed = TRUE)
      out
    },
    character(1)
  )
}
```

```{=html}
<!-- TODO: investigate rotating the page number on the landscape page (not sure
     if standard). One approach: \usepackage{everypage} + \tikz overlay in the
     header; another is lscape + rotating package. -->
```

```{=latex}
\begin{landscape}
```

```{r tbl-overview}
#| tbl-cap: "Predicted $P_{\\mathrm{corr}}$ at key trial positions and test--control contrasts for all experiments. Control start and contrast columns are blank for test-only experiments."
#| eval: !expr knitr::pandoc_to() != "docx"

knitr::asis_output(tblOverviewStr)
```

```{=latex}
\end{landscape}
```

```{r tbl-sample-sizes}
#| tbl-cap: "Per-experiment sample sizes and test-phase duration. Wasps and choices are split by phase (test and control). Last trial is the highest trial number reached in the test phase. Control columns are blank for test-only experiments."
#| eval: !expr knitr::pandoc_to() != "docx"

knitr::asis_output(tblSampleSizesStr)
```

```{r tbl-model-coefs}
#| tbl-cap: "Model coefficients for all experiments. Fixed effects: trial number, reward side, and (for experiments with a control phase) experiment phase (manipulation) and its interaction with trial number. Random effect: individual ID."
#| eval: !expr knitr::pandoc_to() != "docx"
knitr::asis_output(tblModelCoefsStr)
```

## Additional experiments

```{r fig-supp-experiments}
#| fig-height: 4
#| fig-cap: "Wasp performance for two additional \"control\" experiments not included in the main analysis. A. To rule out the possibility that above-chance discrimination of dorsal stimuli might be explained by the use of reflections of the dorsal stimuli off surfaces of the Y-maze that are ventral or lateral to the wasps (i.e. the bottom and sides of the maze) we tested whether wasps could discriminate the thick oblique artificial stimuli after covering first the bottom (middle panel) and then the sides of the maze (right panel) with LEE Filter 1/4 white diffuser film (251). Note that performance remains well above chance after the addition of the diffuser. B. In this experiment we first tested whether a group of wasps could discriminate a naturalistic pair of stimuli (left panel, same data as presented in @{fig-q3-tc} row 6). To rule out that performance differences between naturalistic and artificial stimuli might be driven by differences in wasp species, hives, individuals or phase of the season, we tested if the same group of wasps could discriminate the perpendicular-parallel artificial stimuli (right panel) immediately following a naturalistic canopy stimulus pair (left panel). Note that the same wasp individuals that could not discriminate the naturalistic stimuli can discriminate the artificial stimuli."
#| 
#| 
#| eval: !expr knitr::pandoc_to() != "docx"
print(suppFig)
```

## Canopy G (pilot)

```{r fig-supp-canopyG1}
#| fig-cap: "Wasp reward-navigation performance for the Canopy G (pilot) naturalistic stimulus experiment. This was a \"pilot\" canopy experiment that we later repeated with an increased number of trials (canopy G in @{fig-q3-tc}). The panels show wasp performance over the test and control phases of the experiment. All other figure conventions as in @fig-q3-tc."
#| fig-height: 2

print(fig_supp_canopyG1)
```
