---
title: "glm_analysis"
format:
  pdf: default
  latex:
    fig-format: pdf
  docx:
    fig-dpi: 300
    reference-doc: reference.docx
execute:
  dir: project
header-includes:
  - \usepackage{caption}
  - \captionsetup{format=plain, labelsep=period, justification=justified, singlelinecheck=false}
editor:
  markdown:
    wrap: 72
---

```{r setupQuarto, echo=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)

if (knitr::pandoc_to("docx")) {
  dev_docx <- if (requireNamespace("ragg", quietly = TRUE)) "ragg_png" else "png"
  knitr::opts_chunk$set(
    dev = dev_docx,
    dpi = 300,
    fig.retina = 1
  )
}
```

```{r loadResults, include=FALSE}
# Load pre-computed and formatted results.
# To regenerate: run run_analysis.R then format_results.R from the project root.
library(tidyverse)
library(scales)
source("functions/format_numeric_cols.R")

load("scripts/glm_analysis/formatted_results.RData")

# Display name lookups. Keys are raw experiment IDs; values are display names.
artLabels <- c(
  perpPara_170725 = "Perp/para",
  thinOb_150823   = "Oblique \u00b145\u00b0",
  brightDiff_250725 = "Transp./opaque"
)

natcanLabels <- c(
  natcan1_170923 = "Canopy D",
  natcan2_300725 = "Canopy E",
  natcan3_080825 = "Canopy F1",
  natcan3_190925 = "Canopy F2",
  natcan4_180825 = "Canopy G",
  natcan5_290825 = "Canopy H",
  natcan6_070925 = "Canopy I"
)
```

# Question 1: Can wasps discriminate a 'simple' artificial dorsal pattern?

Evidence that wasps can use overhead patterns comes from two
observations. First, That the proportion of choices for the rewarding
pattern ($P_{\mathrm{corr}}$) is \>50% and second, that this proportion drops when the patterns are removed from the roof
(during the control).

```{r fig-q1}
#| fig-cap: 'Wasp reward navigation performance during the test and control phases of the perpendicular-parallel Y-maze experiment. During the test phase perpendicular and parallel overhead stimuli could be used by the wasps to choose which of two chambers held the reward, but during the subsequent control these stimuli were removed. The y-axis represents the proportion of all entries ("choices") that were into the rewarding ("correct") chamber. The solid black line represents the predicted mean proportion of correct decisions across trial number and the grey ribbon the 95% confidence interval around these predictions provided by the model. Grey points represent the rolling mean of the proportion of correct choices in 3-trial wide windows across all wasps present in those trials. Black points represent the predicted proportion of correct choices at the end of the test and the start of the control phases, and the error bars the 95% confidence intervals around these predictions. Only the first choice of each wasp in each trial was used as data in the model and to calculate the rolling means. The dashed horizontal line represents chance performance (50%).'

q1ID <- "perpPara_170725"
mCoefsRefQ1    <- tcRes$mCoefsRef[q1ID, , drop = FALSE]
contrastsRefQ1 <- tcRes$contrastsRef[q1ID, , drop = FALSE]
emmPtsRefQ1    <- emmPtsRef[q1ID, , drop = FALSE]
emmPtsQ1          <- emmPts %>% filter(experiment == q1ID,
                                       trial_pos %in% c("last_test", "ctrl_start")) 
emmAllQ1          <- emmAll %>% filter(experiment == q1ID)

df_rolling <- choices_rolling %>% filter(experiment == q1ID)

p <- ggplot(data = emmAllQ1, aes(x = rank_trial))+
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL), alpha = 0.2) +
  geom_line(aes(x = rank_trial, y = prob)) +
  labs(x = "Trial", y = "% of decisions for reward")+
  scale_y_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.1))+
  geom_hline(yintercept = 0.5, lty = 2)+
  plotStyle$themeTextEnlarged+
  facet_wrap(vars(manipulation))#+ cant make spacing 0 as x labels overlap
  #theme(panel.spacing.x = unit(0, "lines"))

p <- p + geom_point(data = df_rolling, aes(x = rank_trial, y = pcorr),
                    colour = "black", alpha = 0.1)

p <- p +
  geom_errorbar(data = emmPtsQ1,
                aes(x = rank_trial, ymin = asymp.LCL, ymax = asymp.UCL),
                width = 2) +
  geom_point(data = emmPtsQ1, aes(x = rank_trial, y = prob))

p


```

During the test phase, trial number had a significant positive effect on
$P_{\mathrm{corr}}$ (@fig-q1, solid line; p`r mCoefsRefQ1$rank_trial_pFmt`),
with $P_{\mathrm{corr}}$ rising from `r emmPtsRefQ1$first_prob` (95% CI
`r emmPtsRefQ1$first_confint`) at trial 1 to `r emmPtsRefQ1$last_test_prob`
(95% CI `r emmPtsRefQ1$last_test_confint`) by test end.

End-of-test $P_{\mathrm{corr}}$ was significantly above chance (lower 95% CI
bound \>50%; @fig-q1 test panel), and significantly above performance at the
start of the control phase (`r emmPtsRefQ1$ctrl_start_prob`, 95% CI
`r emmPtsRefQ1$ctrl_start_confint`; p`r contrastsRefQ1$pFmt`; @fig-q1).

Also note that $P_{\mathrm{corr}}$ is significantly above chance (grey
shaded 95% confidence ribbon in @fig-q1 does not overlap the 50% line)
from an early trial number and remains that way until the end of the
test. In contrast, the $P_{\mathrm{corr}}$ in the control phase is never
significantly above chance for the duration of the control (95%
confidence ribbon overlaps the 50% line), as one would expect for wasps
making choices in the absence of any information regarding the location
of the reward.

That the model suggests naive wasps perform above chance at the onset of
the test phase (ie. in trial 1) can be attributed to the fact that the
model is unable to fit the rapid learning of the wasps, rather than to
the availability and learning of olfactory and / or temporal cues during
the pre-test training phase. This is supported by the proportion of
correct decisions in the first few 3-trial wide windows of the test
phase (black points) that are clustered around 50%.

```{r q1Cleanup}
rm(
  q1ID, mCoefsRefQ1, contrastsRefQ1,
  emmPtsRefQ1, emmPtsQ1, emmAllQ1,
  df_rolling, p
)
```

# Question 2: What information are wasps using to discriminate patterns?

```{r fig-q2}
#| fig-cap: 'Wasp reward navigation performance for two additional artificial stimulus experiments. Top: oblique stripes experiment, in which wasps could use overhead stripe stimuli oriented at 45 degrees to the left or right of the maze arm to choose the rewarding chamber during the test phase; stimuli were removed during the subsequent control phase. Bottom: brightness difference experiment, in which wasps could use an opaque versus transparent roof to discriminate chambers; this experiment had no control phase. The y-axis represents the proportion of all entries ("choices") that were into the rewarding ("correct") chamber. The solid black line represents the predicted mean proportion of correct decisions across trial number and the grey ribbon the 95% confidence interval around these predictions provided by the model. Grey points represent the rolling mean of the proportion of correct choices in 3-trial wide windows across all wasps present in those trials. Black points represent the predicted proportion of correct choices at the end of the test and the start of the control phases (oblique stripes only), and the error bars the 95% confidence intervals around these predictions. Only the first choice of each wasp in each trial was used as data in the model and to calculate the rolling means. The dashed horizontal line represents chance performance (50%).'

q2ExpOrder <- c("thinOb_150823", "brightDiff_250725")

emmArtPlotAll <- emmAll %>%
  filter(experiment %in% q2ExpOrder) %>%
  mutate(
    experiment = recode(experiment, !!!artLabels),
    experiment = factor(experiment, levels = unname(artLabels[q2ExpOrder])),
    manipulation = factor(manipulation, levels = c("test", "control"))
  )

p <- ggplot(emmArtPlotAll, aes(x = rank_trial, y = prob)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL), alpha = 0.2) +
  geom_line() +
  labs(x = "Trial", y = "% of decisions for reward") +
  scale_y_continuous(labels = scales::percent) +
  geom_hline(yintercept = 0.5, lty = 2) +
  plotStyle$themeTextEnlarged +
  facet_grid(experiment ~ manipulation, scales = "free_x") +
  theme(panel.spacing.y = unit(1, "lines"),
        panel.spacing.x = unit(0, "lines")
)

df_rolling <- choices_rolling %>%
  filter(experiment %in% q2ExpOrder) %>%
  mutate(
    experiment = recode(experiment, !!!artLabels),
    experiment = factor(experiment, levels = unname(artLabels[q2ExpOrder])),
    manipulation = factor(manipulation, levels = c("test", "control"))
  )

p <- p + geom_point(data = df_rolling, aes(x = rank_trial, y = pcorr),
                    colour = "black", alpha = 0.1)

emmPtsQ2 <- emmPts %>%
  filter(experiment %in% q2ExpOrder,
         trial_pos %in% c("last_test", "ctrl_start")) %>%
  mutate(
    experiment = recode(experiment, !!!artLabels),
    experiment = factor(experiment, levels = unname(artLabels[q2ExpOrder]))
  )

p <- p +
  geom_errorbar(data = emmPtsQ2,
                aes(x = rank_trial, ymin = asymp.LCL, ymax = asymp.UCL),
                width = 2) +
  geom_point(data = emmPtsQ2, aes(x = rank_trial, y = prob))

p

# table used in Q2 inline writing
emmArt <- emmPtsRef %>%
  tibble::rownames_to_column("experiment") %>%
  filter(nat_or_art == "artificial") %>%
  tibble::column_to_rownames("experiment")
```

```{r q2ContrastArtStimuli}
q2ArtTableOrder <- c("perpPara_170725", "thinOb_150823", "brightDiff_250725")

q2TrialSlopeTable <- bind_rows(
    tcRes$trialSlopeRef  %>% tibble::rownames_to_column("experiment"),
    testRes$trialSlopeRef %>% tibble::rownames_to_column("experiment")
  ) %>%
  filter(nat_or_art == "artificial") %>%
  select(-nat_or_art) %>%
  tibble::column_to_rownames("experiment")

q2ArtTcContrastTable <- tcRes$contrastsTbl %>%
  filter(nat_or_art == "artificial") %>%
  mutate(experiment = forcats::fct_relevel(experiment, q2ArtTableOrder)) %>%
  arrange(experiment) %>%
  select(
    experiment,
    logOddsRatio95CI,
    pFmt,
    testEndTrial
  ) %>%
  rename(
    `Experiment` = experiment,
    `Log-odds ratio [95% CI]` = logOddsRatio95CI,
    `P` = pFmt,
    `Test end trial` = testEndTrial
  )

# Build combined model table (artificial + naturalistic) for supplementary
suppArtModelData <- bind_rows(tcRes$mCoefsTbl, testRes$mCoefsTbl) %>%
  filter(nat_or_art == "artificial") %>%
  mutate(experiment = forcats::fct_relevel(experiment, q2ArtTableOrder)) %>%
  arrange(experiment, term)

suppNatModelData <- bind_rows(tcRes$mCoefsTbl, testRes$mCoefsTbl) %>%
  filter(nat_or_art == "naturalistic") %>%
  mutate(
    experiment = recode(experiment, !!!natcanLabels),
    experiment = factor(experiment, levels = unname(natcanLabels))
  ) %>%
  arrange(experiment, term)

suppModelData <- bind_rows(suppArtModelData, suppNatModelData)

# Group anchors for pack_rows — art block
suppArtModelGroups <- suppArtModelData %>%
  group_by(experiment) %>%
  summarise(n = n(), .groups = "drop") %>%
  mutate(
    end   = cumsum(n),
    start = end - n + 1,
    label = unname(artLabels[as.character(experiment)])
  )

# Group anchors for pack_rows — nat block (row indices continue after art block)
artNRows <- nrow(suppArtModelData)
suppNatModelGroups <- suppNatModelData %>%
  group_by(experiment) %>%
  summarise(n = n(), .groups = "drop") %>%
  mutate(
    end   = artNRows + cumsum(n),
    start = end - n + 1,
    label = as.character(experiment)
  )

suppModelTable <- suppModelData %>%
  select(term, logOdds95CI, pFmt) %>%
  rename(
    `Term`              = term,
    `Log-odds [95% CI]` = logOdds95CI,
    `P`                 = pFmt
  )
```

To answer whether wasps require optic flow information to discriminate
patterns we tested whether they could distinguish a new artificial
pattern-pair, one consisting of oblique stripes oriented at either 45
degrees to the right or to the left of the y-maze arm's long axis and
the general direction of wasp travel. Here again, evidence that wasps
can distinguish stimuli that generate identical rates of optic flow is
evidenced by a $P_{\mathrm{corr}}$ \>50% and a larger
$P_{\mathrm{corr}}$ at the end of the test relative to the start of the
control.

Wasps had no trouble distinguishing between oblique stripes that
presumably produce identical rates of optic flow in the dorsal visual
field (@fig-q2). Similar to the perpendicular-parallel experiment, trial
had a significant positive effect on $P_{\mathrm{corr}}$
(p`r q2TrialSlopeTable["thinOb_150823", "pFmt"]`; @tbl-s-model-coefs),
with performance rising from `r emmArt["thinOb_150823", "first_prob"]`
(95% CI `r emmArt["thinOb_150823", "first_confint"]`) at trial 1 to
`r emmArt["thinOb_150823", "last_test_prob"]` (95% CI
`r emmArt["thinOb_150823", "last_test_confint"]`) by test end —
significantly above chance (50%). $P_{\mathrm{corr}}$ at test end was also significantly above performance
at the start of the control phase (`r emmPtsRef["thinOb_150823", "ctrl_start_prob"]`,
95% CI `r emmPtsRef["thinOb_150823", "ctrl_start_confint"]`;
p`r tcRes$contrastsRef["thinOb_150823","pFmt"]`).

Next, we asked whether wasps could discriminate between an opaque and
transparent roof, ie. between stimuli that carried little to no pattern
information. Trial had a positive but non-significant effect on $P_{\mathrm{corr}}$
(p`r q2TrialSlopeTable["brightDiff_250725", "pFmt"]`; @tbl-s-model-coefs),
likely due to the shorter number of trials run in this experiment, and
performance rose from `r emmArt["brightDiff_250725", "first_prob"]`
(95% CI `r emmArt["brightDiff_250725", "first_confint"]`) at trial 1 to
`r emmArt["brightDiff_250725", "last_test_prob"]`
(95% CI `r emmArt["brightDiff_250725", "last_test_confint"]`) by test end. Performance at
the end of the experiment is only borderline significantly higher than
50% because of the increased uncertainty in the slope / effect of trials
on performance due to the lower number of trials run in this experiment.
However, if one uses other metrics or analyses to compare performance to
the 50% line, they are significantly different (for example, comparing
performance at an intermediate trial or comparing the average
performance of the last five trials to the 50% line).

```{r tbl-q2-art-contrast}
#| tbl-cap: "Artificial test-control contrasts (test end vs control start)."
knitr::kable(
  q2ArtTcContrastTable,
  booktabs = TRUE
)
```

# Question 3: Can wasps use naturalistic patterns for navigation?

Evidence for whether wasps can discriminate naturalistic canopies at
above-chance rates (\>50%) is mixed. In four of the seven naturalistic
canopy pairs we tested, the predicted $P_{\mathrm{corr}}$ by the end of
the experiment was significantly above chance (the lower limit of the
95% CI is \>50%, see @tbl-q3-nat-tc-pts), suggesting wasps may be
able to separate certain pairs of naturalistic canopies, although the performance is generally lower than for artificial stimuli (see below).

```{r fig-q3-tc}
#| fig-cap: "Naturalistic test-control performance over trials."
#| fig-height: 6

emmNatTcAll <- emmAll %>%
  filter(nat_or_art == "naturalistic") %>%
  mutate(experiment = recode(experiment, !!!natcanLabels))
emmNatTcPts <- emmPts %>%
  filter(nat_or_art == "naturalistic",
         trial_pos %in% c("last_test", "ctrl_start")) %>%
  mutate(experiment = recode(experiment, !!!natcanLabels))
tbNatTcPts  <- emmPtsRef %>% filter(nat_or_art == "naturalistic")

choicesRollTc <- choices_rolling %>%
  filter(nat_or_art == "naturalistic") %>%
  mutate(experiment = recode(experiment, !!!natcanLabels))

p <- ggplot(emmNatTcAll, aes(x = rank_trial, y = prob)) +
  geom_line() +
  geom_ribbon(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    alpha = 0.15,
    colour = NA
  ) +
  ylim(0, 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  facet_grid(experiment ~ manipulation, scales = "free_x") +
  ylab("P(correct)") +
  theme_bw() +
  theme(legend.position = "none", panel.spacing.y = unit(0.75, "lines"),
        panel.spacing.x = unit(0, "lines"))

p <- p + geom_point(data = choicesRollTc, aes(x = rank_trial, y = pcorr),
                    colour = "black", alpha = 0.1)

p <- p +
  geom_errorbar(data = emmNatTcPts,
                aes(x = rank_trial, ymin = asymp.LCL, ymax = asymp.UCL),
                width = 2) +
  geom_point(data = emmNatTcPts, aes(x = rank_trial, y = prob))

p
```

```{r q3Table}
q3NatPtsTable <- emmPtsTbl %>%
  filter(nat_or_art == "naturalistic") %>%
  mutate(
    experiment = recode(experiment, !!!natcanLabels),
    experiment = factor(experiment, levels = unname(natcanLabels))
  ) %>%
  arrange(experiment) %>%
  select(experiment, lastTestPcorr95CI, ctrlStartPcorr95CI, lastTestTrial)

q3NatTcContrastTable <- tcRes$contrastsTbl %>%
  filter(nat_or_art == "naturalistic") %>%
  mutate(
    experiment = recode(experiment, !!!natcanLabels),
    experiment = factor(experiment, levels = unname(natcanLabels))
  ) %>%
  arrange(experiment) %>%
  select(experiment, logOddsRatio95CI, pFmt, testEndTrial) %>%
  rename(
    `Experiment` = experiment,
    `Log-odds ratio [95% CI]` = logOddsRatio95CI,
    `P` = pFmt,
    `Test end trial` = testEndTrial
  )
```

```{r tbl-q3-nat-tc-pts}
#| tbl-cap: "Naturalistic test-control performance at test end and control start."
knitr::kable(
  q3NatPtsTable,
  booktabs = TRUE
)
```

Of the four naturalistic canopies that show $P_{\mathrm{corr}}$ \> 50%, after three of those we also ran a control (patterns removed) directly after the test phase concluded, but in only one case (Canopy D) was the $P_{\mathrm{corr}}$ at the end of the test significantly higher than at the start of the control. This can be attributed to the fact that $P_{\mathrm{corr}}$ for the naturalistic
canopies is generally not much greater than 50% (if at all), and the
fact that control experiments were not run for many trials, increasing
the uncertainty around the $P_{\mathrm{corr}}$ during the control phase.

```{r tbl-q3-nat-tc-contrast}
#| tbl-cap: "Naturalistic test-control contrasts (test end vs control start)."
knitr::kable(
  q3NatTcContrastTable,
  booktabs = TRUE
)
```

Of the four naturalistic canopies that show $P_{\mathrm{corr}}$ \> 50%, after three of those we also ran a control (patterns removed) directly after the test phase concluded, but in only one case (Canopy D) was the $P_{\mathrm{corr}}$ at the end of the test significantly higher than at the start of the control. This can be attributed to the fact that $P_{\mathrm{corr}}$ for the naturalistic
canopies is generally not much greater than 50% (if at all), and the
fact that control experiments were not run for many trials, increasing
the uncertainty around the $P_{\mathrm{corr}}$ during the control phase.

```{r fig-q3-natart}
#| fig-cap: "End-of-test predicted performance by canopy type."

q3NatArtEndPts <- emmPts %>%
  filter(trial_pos == "last_test") %>%
  mutate(
    nat_or_art = factor(nat_or_art, levels = c("naturalistic", "artificial"))
  )

natArtMean <- q3NatArtEndPts %>%
  group_by(nat_or_art) %>%
  summarise(
    mean_prob = mean(prob),
    min_prob  = min(prob),
    max_prob  = max(prob),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from  = nat_or_art,
    values_from = c(mean_prob, min_prob, max_prob),
    names_glue  = "{nat_or_art}_{.value}"
  ) %>%
  mutate(diff_mean_prob = artificial_mean_prob - naturalistic_mean_prob) %>%
  fmtNumCols()

q3NatBest  <- q3NatArtEndPts %>%
  filter(nat_or_art == "naturalistic") %>%
  slice_max(order_by = prob, n = 1, with_ties = FALSE) %>%
  fmtNumCols()

q3ArtWorst <- q3NatArtEndPts %>%
  filter(nat_or_art == "artificial") %>%
  slice_min(order_by = prob, n = 1, with_ties = FALSE) %>%
  fmtNumCols()

ptJitter   <- position_jitter(width = 0.08, height = 0, seed = 3)
canopyCols <- c(naturalistic = "forestgreen", artificial = "black")

ggplot(q3NatArtEndPts, aes(x = nat_or_art, y = prob)) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_boxplot(aes(color = nat_or_art), width = 0.2, outlier.shape = NA) +
  geom_errorbar(
    aes(ymin = asymp.LCL, ymax = asymp.UCL, color = nat_or_art),
    width = 0.03, alpha = 0.3, position = ptJitter
  ) +
  geom_point(aes(color = nat_or_art), size = 2, alpha = 0.1, position = ptJitter) +
  scale_color_manual(values = canopyCols, guide = "none") +
  scale_y_continuous(limits = c(0, 1)) +
  labs(x = "Canopy type", y = "Predicted P(correct) at end of test") +
  theme_bw()
```

*Performance differences among naturalistic and artificial stimuli*

Discrimination performance for naturalistic canopies tends
to be lower than for artificial canopies. The naturalistic canopy
showing the best performance (`r q3NatBest$experiment`,
$P_{\mathrm{corr}}$ = `r q3NatBest$prob`) still has a lower
$P_{\mathrm{corr}}$ than the artificial canopy with the worst
performance (`r q3ArtWorst$experiment`, $P_{\mathrm{corr}}$ =
`r q3ArtWorst$prob`). The average performance for all naturalistic
canopies is `r natArtMean$naturalistic_mean_prob`, whereas for
artificial it is `r natArtMean$artificial_mean_prob`, and the difference
in the average $P_{\mathrm{corr}}$ for naturalistic and artificial is
`r natArtMean$diff_mean_prob`. Given the low number of artificial and
naturalistic experiments included here (n = 3 and 7 respectively) we did
not test for an overall difference between naturalistic and artificial
canopies.

# Supplementary

```{r supplementaryTbls}
roundNumsInString <- function(x, digits = 2) {
  vapply(
    x,
    function(s) {
      nums <- regmatches(s, gregexpr("-?[0-9]+\\.?[0-9]*", s, perl = TRUE))[[1]]
      if (length(nums) == 0) return(s)
      out     <- s
      rounded <- sprintf(paste0("%.", digits, "f"), as.numeric(nums))
      for (i in seq_along(nums)) out <- sub(nums[i], rounded[i], out, fixed = TRUE)
      out
    },
    character(1)
  )
}

s1PtsTbl <- emmPtsTbl %>%
  mutate(
    across(c(firstPcorr95CI, midPcorr95CI, lastTestPcorr95CI, ctrlStartPcorr95CI),
           ~ roundNumsInString(.x, digits = 2)),
    `last test trial` = lastTestTrial
  ) %>%
  select(-lastTestTrial)

trialSlopeTbl <- bind_rows(testRes$trialSlopeTbl, tcRes$trialSlopeTbl)

allContrastsTbl <- bind_rows(q2ArtTcContrastTable, q3NatTcContrastTable)

suppTbls <- list(
  "Predictions at first, middle, last test, and control start" = s1PtsTbl,
  "Test-control contrasts (test end vs control start)"         = allContrastsTbl,
  "Trial slope summary"                                        = trialSlopeTbl
)

purrr::iwalk(suppTbls, function(tbl, cap) {
  print(knitr::kable(tbl, caption = cap, booktabs = TRUE))
  cat("\n\n")
})
```

```{r tbl-s-model-coefs}
#| tbl-cap: "Model coefficients for all stimulus experiments."
k <- knitr::kable(suppModelTable, booktabs = TRUE)
allGroups <- bind_rows(suppArtModelGroups, suppNatModelGroups)
for (i in seq_len(nrow(allGroups))) {
  k <- kableExtra::pack_rows(k,
    allGroups$label[i],
    allGroups$start[i],
    allGroups$end[i]
  )
}
k
```
