---
title: "glm_analysis"
format:
  pdf: default
  latex:
    fig-format: pdf
  docx:
    fig-dpi: 300
    reference-doc: reference.docx
execute:
  dir: project
header-includes:
  - \usepackage{caption}
  - \captionsetup{format=plain, labelsep=period, justification=justified, singlelinecheck=false}
editor:
  markdown:
    wrap: 72
---

```{r setupQuarto, echo=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)

if (knitr::pandoc_to("docx")) {
  dev_docx <- if (requireNamespace("ragg", quietly = TRUE)) "ragg_png" else "png"
  knitr::opts_chunk$set(
    dev = dev_docx,
    dpi = 300,
    fig.retina = 1
  )
}
```

```{r loadResults, include=FALSE}
# Load pre-computed and formatted results.
# To regenerate: run run_analysis.R then format_results.R from the project root.
library(tidyverse)
library(scales)
source("functions/format_numeric_cols.R")

load("scripts/glm_analysis/formatted_results.RData")
```

# Question 1: Can wasps discriminate a 'simple' artificial dorsal pattern?

Evidence that wasps can use overhead patterns comes from two
observations. First, That the proportion of choices for the rewarding
pattern is \>50% and second, that this proportion of decisions for the
rewarding patterns drops when the patterns are removed from the roof
(during the control).

```{r fig-q1}
#| fig-cap: 'Wasp reward navigation performance during the test and control phases of the perpendicular-parallel Y-maze experiment. During the test phase perpendicular and parallel overhead stimuli could be used by the wasps to choose which of two chambers held the reward, but during the subsequent control these stimuli were removed. The y-axis represents the proportion of all entries ("choices") that were into the rewarding ("correct") chamber. The solid black line represents the predicted mean proportion of correct decisions across trial number and the grey ribbon the 95% confidence interval around these predictions provided by the model. Grey points represent the rolling mean of the proportion of correct choices in 3-trial wide windows across all wasps present in those trials. Black points represent the predicted proportion of correct choices at the end of the test and the start of the control phases, and the error bars the 95% confidence intervals around these predictions. Only the first choice of each wasp in each trial was used as data in the model and to calculate the rolling means. The dashed horizontal line represents chance performance (50%).'

q1ID <- "perpPara_170725"
mCoefsInLineQ1    <- tcRes$mCoefsInLine[q1ID, , drop = FALSE]
contrastsInLineQ1 <- tcRes$contrastsInLine[q1ID, , drop = FALSE]
emmPtsInLineQ1    <- emmPtsInLine[q1ID, , drop = FALSE]
emmPtsQ1          <- emmPts %>% filter(experiment == q1ID)
emmAllQ1          <- emmAll %>% filter(experiment == q1ID)

df_rolling <- choices_rolling %>% filter(experiment == q1ID)

p <- ggplot(data = emmAllQ1, aes(x = rank_trial))+
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL), alpha = 0.2) +
  geom_line(aes(x = rank_trial, y = prob)) +
  labs(x = "Trial", y = "% of decisions for reward")+
  scale_y_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.1))+
  geom_hline(yintercept = 0.5, lty = 2)+
  plotStyle$themeTextEnlarged+
  facet_wrap(vars(manipulation))

p <- p + geom_point(data = df_rolling, aes(x = rank_trial, y = pcorr),
                    colour = "black", alpha = 0.1)

p <- p +
  geom_errorbar(data = emmPtsQ1,
                aes(x = rank_trial, ymin = asymp.LCL, ymax = asymp.UCL),
                width = 2) +
  geom_point(data = emmPtsQ1, aes(x = rank_trial, y = prob))

p
```

During the test phase of the experiment, trial number (experience) had a
significant positive effect on the expected probability
($P_{\mathrm{corr}}$) of a correct decision (@fig-q1, solid line) with
every successive trial increasing the log odds of a correct decision by
`r mCoefsInLineQ1$rank_trial_logOdds` (95% CI
`r mCoefsInLineQ1$rank_trial_confint`,
p`r mCoefsInLineQ1$rank_trial_pFmt`).

The $P_{\mathrm{corr}}$ of a correct choice at the end of the test was
$P_{\mathrm{corr}}$ = `r emmPtsInLineQ1$last_test_prob` (95% CI
`r emmPtsInLineQ1$last_test_confint`), which is significantly higher than chance as implied by the lower bound of the 95%
confidence interval for $P_{\mathrm{corr}}$ being \>50% (black
error bar in the @fig-q1 test panel does not overlap the horizontal dashed
line). Furthermore, the $P_{\mathrm{corr}}$ at the end of the experiment
was also significantly higher than at the start of the control
($P_{\mathrm{corr}}$ = `r emmPtsInLineQ1$ctrl_start_prob`, 95% CI
`r emmPtsInLineQ1$ctrl_start_confint`), and this difference was
significant (log odds ratio = `r contrastsInLineQ1$logOddsRatio`, p
`r contrastsInLineQ1$pFmt`) (@fig-q1, note lack of overlap of error bars
between test and control panel).

Also note that $P_{\mathrm{corr}}$ is significantly above chance (grey
shaded 95% confidence ribbon in @fig-q1 does not overlap the 50% line)
from an early trial number and remains that way until the end of the
test. In contrast, the $P_{\mathrm{corr}}$ in the control phase is never
significantly above chance for the duration of the control (95%
confidence ribbon overlaps the 50% line), as one would expect for wasps
making choices in the absence of any information regarding the location
of the reward.

That the model suggests naive wasps perform above chance at the onset of
the test phase (ie. in trial 1) can be attributed to the fact that the
model is unable to fit the rapid learning of the wasps, rather than to
the availability and learning of olfactory and / or temporal cues during
the pre-test training phase. This is supported by the proportion of
correct decisions in the first few 3-trial wide windows of the test
phase (black points) that are clustered around 50%.

```{r q1Cleanup}
rm(
  q1ID, mCoefsInLineQ1, contrastsInLineQ1,
  emmPtsInLineQ1, emmPtsQ1, emmAllQ1,
  df_rolling, p
)
```

# Question 2: What information are wasps using to discriminate patterns?

```{r fig-q2}
#| fig-cap: 'Wasp reward navigation performance for two additional artificial stimulus experiments. Top: oblique stripes experiment, in which wasps could use overhead stripe stimuli oriented at 45 degrees to the left or right of the maze arm to choose the rewarding chamber during the test phase; stimuli were removed during the subsequent control phase. Bottom: brightness difference experiment, in which wasps could use an opaque versus transparent roof to discriminate chambers; this experiment had no control phase. The y-axis represents the proportion of all entries ("choices") that were into the rewarding ("correct") chamber. The solid black line represents the predicted mean proportion of correct decisions across trial number and the grey ribbon the 95% confidence interval around these predictions provided by the model. Grey points represent the rolling mean of the proportion of correct choices in 3-trial wide windows across all wasps present in those trials. Black points represent the predicted proportion of correct choices at the end of the test and the start of the control phases (oblique stripes only), and the error bars the 95% confidence intervals around these predictions. Only the first choice of each wasp in each trial was used as data in the model and to calculate the rolling means. The dashed horizontal line represents chance performance (50%).'

q2ExpOrder <- c("thinOb_150823", "brightDiff_250725")

emmArtPlotAll <- emmAll %>%
  filter(experiment %in% q2ExpOrder) %>%
  mutate(
    experiment = factor(experiment, levels = q2ExpOrder),
    manipulation = factor(manipulation, levels = c("test", "control"))
  )

p <- ggplot(emmArtPlotAll, aes(x = rank_trial, y = prob)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL), alpha = 0.2) +
  geom_line() +
  labs(x = "Trial", y = "% of decisions for reward") +
  scale_y_continuous(labels = scales::percent) +
  geom_hline(yintercept = 0.5, lty = 2) +
  plotStyle$themeTextEnlarged +
  facet_grid(experiment ~ manipulation, scales = "free_x")

df_rolling <- choices_rolling %>%
  filter(experiment %in% q2ExpOrder) %>%
  mutate(
    experiment = factor(experiment, levels = q2ExpOrder),
    manipulation = factor(manipulation, levels = c("test", "control"))
  )

p <- p + geom_point(data = df_rolling, aes(x = rank_trial, y = pcorr),
                    colour = "black", alpha = 0.1)

emmPtsQ2 <- emmPts %>%
  filter(experiment %in% q2ExpOrder,
         trial_pos %in% c("last_test", "ctrl_start")) %>%
  mutate(experiment = factor(experiment, levels = q2ExpOrder))

p <- p +
  geom_errorbar(data = emmPtsQ2,
                aes(x = rank_trial, ymin = asymp.LCL, ymax = asymp.UCL),
                width = 2) +
  geom_point(data = emmPtsQ2, aes(x = rank_trial, y = prob))

p

# table used in Q2 inline writing
emmArt <- emmPtsInLine %>%
  tibble::rownames_to_column("experiment") %>%
  filter(nat_or_art == "artificial") %>%
  tibble::column_to_rownames("experiment")
```

```{r q2ContrastArtStimuli}
q2ArtTableOrder <- c("perpPara_170725", "thinOb_150823", "brightDiff_250725")

q2TrialSlopeTable <- testRes$trialSlopeInLine %>%
  filter(nat_or_art == "artificial") %>%
  select(-nat_or_art)

q2ArtTcContrastTable <- tcRes$contrastsMsTab %>%
  filter(nat_or_art == "artificial") %>%
  mutate(experiment = forcats::fct_relevel(experiment, q2ArtTableOrder)) %>%
  arrange(experiment) %>%
  select(
    experiment,
    logOddsRatio95CI,
    pFmt,
    testEndTrial
  ) %>%
  rename(
    `Experiment` = experiment,
    `Log-odds ratio [95% CI]` = logOddsRatio95CI,
    `P` = pFmt,
    `Test end trial` = testEndTrial
  )

q2ArtModelTable <- testRes$mCoefsMsTab %>%
  filter(nat_or_art == "artificial") %>%
  mutate(experiment = forcats::fct_relevel(experiment, q2ArtTableOrder)) %>%
  arrange(experiment, term) %>%
  select(
    experiment,
    term,
    logOdds95CI,
    pFmt
  ) %>%
  rename(
    `Experiment` = experiment,
    `Term` = term,
    `Log-odds [95% CI]` = logOdds95CI,
    `P` = pFmt
  )
```

To answer whether wasps require optic flow information to discriminate
patterns we tested whether they could distinguish a new artificial
pattern-pair, one consisting of oblique stripes oriented at either 45
degrees to the right or to the left of the y-maze arm's long axis and
the general direction of wasp travel. Here again, evidence that wasps
can distinguish stimuli that generate identical rates of optic flow is
evidenced by a $P_{\mathrm{corr}}$ \>50% and a larger
$P_{\mathrm{corr}}$ at the end of the test relative to the start of the
control.

Wasps had no trouble distinguishing between oblique stripes that
presumably produce identical rates of optic flow in the dorsal visual
field (@fig-q2). Similar to the perpendicular-parallel experiment, trial
had a significant positive effect on $P_{\mathrm{corr}}$, with every
successive trial increasing the log odds of a correct decision by
`r q2TrialSlopeTable["thinOb_150823", "logOdds"]` (95% CI
`r q2TrialSlopeTable["thinOb_150823", "confint"]`, p
`r q2TrialSlopeTable["thinOb_150823", "pFmt"]`; @tbl-q2-art-model).
Initially (at trial 1) performance was not significantly different from
chance ($P_{\mathrm{corr}}$ = `r emmArt["thinOb_150823", "first_prob"]`,
95% CI `r emmArt["thinOb_150823", "first_confint"]`) but rose steeply,
reaching `r emmArt["thinOb_150823", "last_test_prob"]` (95% CI
`r emmArt["thinOb_150823", "last_test_confint"]`) by the end of the
experiment (trial 66), which is significantly higher than expected by
chance (50%). $P_{\mathrm{corr}}$ at the end of the test phase of the
experiment was also higher than at the start of the control (log odds ratio = `r tcRes$contrastsInLine["thinOb_150823","logOddsRatio"]`, 95% CI `r tcRes$contrastsInLine["thinOb_150823","confint"]`, p`r tcRes$contrastsInLine["thinOb_150823","pFmt"]`).

Next, we asked whether wasps could discriminate between an opaque and
transparent roof, ie. between stimuli that carried little to no pattern
information. While trial had a positive effect on $P_{\mathrm{corr}}$
(beta = `r q2TrialSlopeTable["brightDiff_250725", "logOdds"]`, 95% CI
`r q2TrialSlopeTable["brightDiff_250725", "confint"]`), unlike for the
other two pairs of artificial stimuli this effect was not significant (p
= `r q2TrialSlopeTable["brightDiff_250725", "pFmt"]`), likely due to the
much shorter number of trials this experiment was run for. While
statistical support for a positive slope is lacking, there is support
for $P_{\mathrm{corr}}$ \> 50% towards the middle and end of the
experiment. At the onset of the experiment (trial 1), wasp performance
was not significantly different from 50% ($P_{\mathrm{corr}}$ =
`r emmArt["brightDiff_250725", "first_prob"]`, 95% CI
`r emmArt["brightDiff_250725", "first_confint"]`) but rises with
experience and by the end of the experiment (trial 26)
$P_{\mathrm{corr}}$ reached `r emmArt["brightDiff_250725", "last_test_prob"]`
(95% CI `r emmArt["brightDiff_250725", "last_test_confint"]`). Performance at
the end of the experiment is only borderline significantly higher than
50% because of the increased uncertainty in the slope / effect of trials
on performance due to the lower number of trials run in this experiment.
However, if one uses other metrics or analyses to compare performance to
the 50% line, they are significantly different (for example, comparing
performance at an intermediate trial or comparing the average
performance of the last five trials to the 50% line).

*Comparison among different artificial stimuli*

```{r tbl-q2-art-contrast}
#| tbl-cap: "Artificial test-control contrasts (test end vs control start)."
knitr::kable(
  q2ArtTcContrastTable,
  booktabs = TRUE
)
```

```{r tbl-q2-art-model}
#| tbl-cap: "Artificial test-model coefficients."
knitr::kable(
  q2ArtModelTable,
  booktabs = TRUE
)
```

# Question 3: Can wasps use naturalistic patterns for navigation?

```{r fig-q3-test}
#| fig-cap: "Naturalistic test performance over trials."
#| fig-height: 8

emmNatTestAll     <- emmAll %>% filter(nat_or_art == "naturalistic", manipulation == "test")
emmNatTestPtsLong <- emmPts %>% filter(nat_or_art == "naturalistic")
emmNatTestPts     <- emmPtsInLine %>% filter(nat_or_art == "naturalistic")

df_rolling <- choices_rolling %>%
  filter(manipulation == "test", nat_or_art == "naturalistic")

```

Evidence for whether wasps can discriminate naturalistic canopies at
above-chance rates (\>50%) is mixed. In four of the seven naturalistic
canopy pairs we tested, the predicted $P_{\mathrm{corr}}$ by the end of
the experiment was significantly above chance (the lower limit of the
95% CI is \>50%, see @tbl-q3-nat-test-pts), suggesting wasps may be
able to separate certain pairs of naturalistic canopies, although the performance is generally lower than for artificial stimuli (see below).

```{r fig-q3-tc}
#| fig-cap: "Naturalistic test-control performance over trials."
#| fig-height: 6


emmNatTcAll <- emmAll %>% filter(nat_or_art == "naturalistic")
emmNatTcPts <- emmPts %>% filter(nat_or_art == "naturalistic")
tbNatTcPts  <- emmPtsInLine %>% filter(nat_or_art == "naturalistic")

expTestAndCtrl <- names(
  which(
    tapply(choices_rolling$manipulation, choices_rolling$experiment,
           function(x) length(unique(x)) > 1)))

choicesRollTc <- choices_rolling %>%
  filter(nat_or_art == "naturalistic" & experiment %in% expTestAndCtrl)

p <- ggplot(emmNatTcAll, aes(x = rank_trial, y = prob)) +
  geom_line() +
  geom_ribbon(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    alpha = 0.15,
    colour = NA
  ) +
  ylim(0, 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  facet_grid(experiment ~ manipulation, scales = "free_x") +
  ylab("P(correct)") +
  theme_bw() +
  theme(legend.position = "none")

p <- p + geom_point(data = choicesRollTc, aes(x = rank_trial, y = pcorr),
                    colour = "black", alpha = 0.1)
p
```

```{r q3Table}
q3NatPtsTable <- emmPtsMsTab %>%
  filter(nat_or_art == "naturalistic") %>%
  select(experiment, lastTestPcorr95CI, ctrlStartPcorr95CI, lastTestTrial)

q3NatTcContrastTable <- tcRes$contrastsMsTab %>%
  filter(nat_or_art == "naturalistic") %>%
  select(experiment, logOddsRatio95CI, pFmt, testEndTrial) %>%
  rename(
    `Experiment` = experiment,
    `Log-odds ratio [95% CI]` = logOddsRatio95CI,
    `P` = pFmt,
    `Test end trial` = testEndTrial
  )
```

```{r tbl-q3-nat-tc-pts}
#| tbl-cap: "Naturalistic test-control performance at test end and control start."
knitr::kable(
  q3NatPtsTable,
  booktabs = TRUE
)
```

Of the four naturalistic canopies that show $P_{\mathrm{corr}}$ \> 50%, after three of those we also ran a control (patterns removed) directly after the test phase concluded, but in only one case (natcan1_170923) was the $P_{\mathrm{corr}}$ at the end of the test significantly higher than at the start of the control. This can be attributed to the fact that $P_{\mathrm{corr}}$ for the naturalistic
canopies is generally not much greater than 50% (if at all), and the
fact that control experiments were not run for many trials, increasing
the uncertainty around the $P_{\mathrm{corr}}$ during the control phase.

```{r tbl-q3-nat-tc-contrast}
#| tbl-cap: "Naturalistic test-control contrasts (test end vs control start)."
knitr::kable(
  q3NatTcContrastTable,
  booktabs = TRUE
)
```

Of the four naturalistic canopies that show $P_{\mathrm{corr}}$ \> 50%, after three of those we also ran a control (patterns removed) directly after the test phase concluded, but in only one case (natcan1_170923) was the $P_{\mathrm{corr}}$ at the end of the test significantly higher than at the start of the control. This can be attributed to the fact that $P_{\mathrm{corr}}$ for the naturalistic
canopies is generally not much greater than 50% (if at all), and the
fact that control experiments were not run for many trials, increasing
the uncertainty around the $P_{\mathrm{corr}}$ during the control phase.

```{r fig-q3-natart}
#| fig-cap: "End-of-test predicted performance by canopy type."

q3NatArtEndPts <- emmPts %>%
  filter(trial_pos == "last_test") %>%
  mutate(
    nat_or_art = factor(nat_or_art, levels = c("naturalistic", "artificial"))
  )

natArtMean <- q3NatArtEndPts %>%
  group_by(nat_or_art) %>%
  summarise(
    mean_prob = mean(prob),
    min_prob  = min(prob),
    max_prob  = max(prob),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from  = nat_or_art,
    values_from = c(mean_prob, min_prob, max_prob),
    names_glue  = "{nat_or_art}_{.value}"
  ) %>%
  mutate(diff_mean_prob = artificial_mean_prob - naturalistic_mean_prob) %>%
  fmtNumCols()

q3NatBest  <- q3NatArtEndPts %>%
  filter(nat_or_art == "naturalistic") %>%
  slice_max(order_by = prob, n = 1, with_ties = FALSE) %>%
  fmtNumCols()

q3ArtWorst <- q3NatArtEndPts %>%
  filter(nat_or_art == "artificial") %>%
  slice_min(order_by = prob, n = 1, with_ties = FALSE) %>%
  fmtNumCols()

ptJitter   <- position_jitter(width = 0.08, height = 0, seed = 3)
canopyCols <- c(naturalistic = "forestgreen", artificial = "black")

ggplot(q3NatArtEndPts, aes(x = nat_or_art, y = prob)) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_boxplot(aes(color = nat_or_art), width = 0.2, outlier.shape = NA) +
  geom_errorbar(
    aes(ymin = asymp.LCL, ymax = asymp.UCL, color = nat_or_art),
    width = 0.03, alpha = 0.3, position = ptJitter
  ) +
  geom_point(aes(color = nat_or_art), size = 2, alpha = 0.1, position = ptJitter) +
  scale_color_manual(values = canopyCols, guide = "none") +
  scale_y_continuous(limits = c(0, 1)) +
  labs(x = "Canopy type", y = "Predicted P(correct) at end of test") +
  theme_bw()
```

*Performance differences among naturalistic and artificial stimuli*

Discrimination performance for naturalistic canopies tends
to be lower than for artificial canopies. The naturalistic canopy
showing the best performance (`r q3NatBest$experiment`,
$P_{\mathrm{corr}}$ = `r q3NatBest$prob`) still has a lower
$P_{\mathrm{corr}}$ than the artificial canopy with the worst
performance (`r q3ArtWorst$experiment`, $P_{\mathrm{corr}}$ =
`r q3ArtWorst$prob`). The average performance for all naturalistic
canopies is `r natArtMean$naturalistic_mean_prob`, whereas for
artificial it is `r natArtMean$artificial_mean_prob`, and the difference
in the average $P_{\mathrm{corr}}$ for naturalistic and artificial is
`r natArtMean$diff_mean_prob`. Given the low number of artificial and
naturalistic experiments included here (n = 3 and 7 respectively) we did
not test for an overall difference between naturalistic and artificial
canopies.

# Supplementary

```{r supplementaryMsTabs}
roundNumsInString <- function(x, digits = 2) {
  vapply(
    x,
    function(s) {
      nums <- regmatches(s, gregexpr("-?[0-9]+\\.?[0-9]*", s, perl = TRUE))[[1]]
      if (length(nums) == 0) return(s)
      out     <- s
      rounded <- sprintf(paste0("%.", digits, "f"), as.numeric(nums))
      for (i in seq_along(nums)) out <- sub(nums[i], rounded[i], out, fixed = TRUE)
      out
    },
    character(1)
  )
}

s1PtsMsTab <- emmPtsMsTab %>%
  mutate(
    across(c(firstPcorr95CI, midPcorr95CI, lastTestPcorr95CI, ctrlStartPcorr95CI),
           ~ roundNumsInString(.x, digits = 2)),
    `last test trial` = lastTestTrial
  ) %>%
  select(-lastTestTrial)

suppMsTabs <- list(
  "Predictions at first, middle, last test, and control start" = s1PtsMsTab,
  "Test-control contrast summary"                              = tcRes$contrastsMsTab,
  "Test trial-slope summary"                                   = testRes$trialSlopeMsTab,
  "Test-control trial-slope summary"                           = tcRes$trialSlopeMsTab,
  "Test model coefficients"                                    = testRes$mCoefsMsTab,
  "Test-control model coefficients"                            = tcRes$mCoefsMsTab
)

purrr::iwalk(suppMsTabs, function(tbl, cap) {
  print(knitr::kable(tbl, caption = cap, booktabs = TRUE))
  cat("\n\n")
})
```
