---
title: "glm_analysis"
format:
  pdf:
    include-in-header:
      text: |
          \usepackage{xspace}
          \newcommand{\Pcorr}{\ensuremath{P_{\mathrm{corr}}}\xspace}
execute:
  dir: project
  
---

```{r setupQuarto, echo=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(
  echo    = FALSE,  # hide code
  message = FALSE,  # hide package messages
  warning = FALSE   # hide warnings
)

```


```{r loadAndCleanChoices, include=FALSE}

# load up the raw data

rm(list = ls())
library(here)
library(lme4)
library(broom.mixed)
library(tidyverse)
library(emmeans)
library(zoo)
library(scales)
source("scripts//loading_cleaning.R")
styleEnv <- new.env(parent = environment())
source("scripts//custom_themes_and_colour_palettes.R", local = styleEnv)

# keep only style objects used in this document
plotStyle <- list(
  themeTextEnlarged = styleEnv$custom_theme_text_enlarged
)
rm(styleEnv)

# removing data that isn't relevant to the main analysis
choices %<>% filter(
  ! experiment %in% c("thick_oblique_apis", "thickOb_140823", "thickObDiff_210924",
                      "perpPara_240723", "perpParaPostNatcan_090925"))

# converting decision to numeric for modelling:
choices$decision <- as.numeric(choices$decision)
# making test the reference level as control always followed (chronologically):
choices$manipulation <- relevel(choices$manipulation, ref = "test")

```


Make the computations necessary for all questions:
```{r buildTestModels}
#| cache: true

# three data structures derived here:
# 1. models and model results 
# 2. emm predictions for all trials
# 3. emm predictions for specific trials 

# classes of models:
# 1. models to look at the test phase of experiments
# 2. models to compare the test and the control phase
# do 1 and 2 really need to have separate model specs? probably just have one 

# 1: models looking at test only
mTest <- choices %>% 
  filter(manipulation == "test") %>%
  split(.$experiment, drop = T) %>%
  # I removed day from the model below because brightDiff experiment causes trouble if its excluded. There is obviously a smarter way around that issue however
  map(~ glmer(
    decision ~ rank_trial + sideAlt_trial + reward_side +
               (1 | individual),
               data = .x, family = binomial))

# get resuls into tidy format
mTestTidy <- map_df(mTest, broom.mixed::tidy, conf.int = T, .id = "experiment")

# find start, mid and end trials from emmeans
emmTestAll <- map2(
  .x = mTest, .y = names(mTest),
  function(m, exp_id) {

    emmeans(m, ~ rank_trial,
            # gets predictions for every trial rather than covariate avg
          cov.keep = "rank_trial", 
          type = "response") %>%
      as.data.frame() %>%
      mutate(experiment = exp_id)
    
})
emmTestAll <- list_rbind(emmTestAll)

# to bring in the nat vs art variable
emmTestAll <- left_join(
  emmTestAll,
  unique(choices[, c("experiment", "nat_or_art")]),
  by = "experiment")

# get start, end and middle of test predictions: 
emmTestPts <- emmTestAll %>% 
  group_by(experiment) %>%
  # get the 'mid trial'
  mutate(mid_trial = ceiling((min(rank_trial) + max(rank_trial)) / 2)) %>%
  filter(rank_trial == max(rank_trial) | rank_trial == 1 |
           rank_trial == mid_trial) %>%
  select(-mid_trial)

```


```{r buildTcModels}
#| cache: false

# four data structures built here:
# 1. models and model results (mTc)
# 2. emm predictions for all trials (emmTcAll)
# 3. emm predictions for specific trials (emmTcPts) 
# 4. emm contrasts between test and control at specific points (contTc)

# 2: run models that look at test and control:
mTc <- choices %>%
  # keep only the experiments that have a test AND control phase
  group_by(experiment) %>%
  filter(n_distinct(manipulation) > 1) %>% 
  # important to drop unused factors otherwise there are lists of experiments with no data
  split(.$experiment, drop = T) %>%
  map( ~ glmer(
    decision ~ rank_trial * manipulation + sideAlt_trial + reward_side +
      (1 | individual),
           data = .x, family = binomial))
# it might be best to run this as one combined model to handle 'day' better. im excluding it for now as i have no idea what impact it would have
# get resuls into tidy format
mTcTidy <- map_df(mTest, broom.mixed::tidy, conf.int = T, .id = "experiment")

# generate predictions for all trials and contrasts for specific trials
emmPredCont <- map2(
  .x = mTc, .y = names(mTc),
  function(m, exp_id) {
    
    # below line allows to only keep predictions from control that actually occur 
    # (in concert w semi-join)
    obs <- model.frame(m) %>% distinct(manipulation, rank_trial) 
    # get test end trial number for contrast test
    testEnd <- max(obs[obs$manipulation == "test",]$rank_trial)
    ctrlStart <- 1
    
    # get predictions for all trials
    emmAll <- emmeans(m, ~ rank_trial * manipulation,
          cov.keep = "rank_trial", # gets predictions for every trial rather than covariate avg
          type = "response") %>%
      as.data.frame() %>%
      semi_join(obs, by = c("manipulation", "rank_trial")) %>%
      mutate(experiment = exp_id)
    
    # get predictions for trials to contrast (end test and start control)
    emmCont <- emmeans(
      m, ~ manipulation * rank_trial,
      at = list(rank_trial = c(ctrlStart, testEnd))
    )
    # exclude end control and start trial predictions
    emmCont <- subset(
      emmCont,
      (manipulation == "control" & rank_trial == ctrlStart) |
      (manipulation == "test"    & rank_trial == testEnd)
    )
    # ChatGPT code below. Make sure order is control@start then test@end
    grid <- emmCont@grid
    # below line sorts first by manipulation (control evaluates to FALSE / zero)
    # then by rank_trial
    ord <- order(grid$manipulation == "test", grid$rank_trial)
    emmCont <- emmCont[ord]

    cont <- contrast(
      emmCont,
      list("test_end - control_start" = c(-1, 1))
    )
    # cont <- pairs(emmCont) This is the alternative to running the custom contrast

    # For reporting, you may want both link-scale test and response-scale summary
    # infer T,T includes confint as well
    contLink <- summary(cont, infer = c(T, T)) %>% 
      rename(logOddsRatio = estimate) %>%
      mutate(
        experiment = exp_id,
        control_start = ctrlStart,
        test_end = testEnd
      )

    contResp <- as.data.frame(summary(cont, type = "response")) %>%
      mutate(
        experiment = exp_id,
        control_start = ctrlStart,
        test_end = testEnd
      )

    list(emmAll = emmAll, contLink = contLink, contResp = contResp)
    
})

# imagine list of lists like a table, this flips rows and cols
emmPredCont <- transpose(emmPredCont) 
# bind the elements within each list together
emmPredCont <- map(emmPredCont, list_rbind)
emmTcAll <- emmPredCont[["emmAll"]]
contTcLn <- emmPredCont[["contLink"]]
contTcRsp <- emmPredCont[["contResp"]]
rm(list = c("emmPredCont"))

# bring in the nat vs art variable
emmTcAll <- left_join(
  emmTcAll,
  unique(choices[, c("experiment", "nat_or_art")]),
  by = "experiment")

# predictions for specific trials (end of the test and the start of the control) 
# by subsetting all trials predictions
emmTcPts <- emmTcAll %>% 
  group_by(nat_or_art, experiment, manipulation) %>%
  filter(manipulation == "test" & rank_trial == max(rank_trial) | 
           manipulation == "control" & rank_trial == 1) 
# the alternative is to use predict and things get real complicated then. 
# honestly i think the reality is actually that predict would work fine, because the other variables in the models hardly have effects?
# and what if i just ran predict on the dataframe itself? didnt i do something like that initially?

```


```{r formatTestDataStructures}
source("functions/format_numeric_cols.R")
source("functions/format_tables.R")

term_labels <- c(
  "(Intercept)"      = "int",
  "rank_trial"       = "trial",
  "reward_sideRight" = "sideR",
  "sideAlt_trialTRUE" = "sideAltT"
)

formattingTablesDir <- "scripts/glm_analysis/formatting_tables/test"
sourceFmt <- function(file) source(file.path(formattingTablesDir, file))

sourceFmt("format_emmTestPts.R") # outputs inLine and MsTab objects 
# outputs inLine and MsTab objects for slope and model generally
sourceFmt("format_mTestTidy.R") 

testRes <- list(
  emmAll = emmTestAll,
  emmPts = emmTestPts,
  emmPtsInLine = emmTestPtsInLine,
  emmPtsMsTab = emmTestPtsMsTab,
  mCoefs = mTestTidy,
  mCoefsInLine = mTestTidyWideInLine,
  mCoefsMsTab = mTestCoefsMsTab,
  trialSlopeInLine = testTrialSlopeInLine,
  trialSlopeMsTab = testTrialSlopeMsTab
)

rm(
  mTest, mTestTidy, mTestTidyInLine, mTestTidyWideInLine,
  testTrialSlopeInLine, testTrialSlopeMsTab, mTestCoefsMsTab,
  emmTestAll, emmTestPts, emmTestPtsInLine,
  term_labels
)

rm(sourceFmt, formattingTablesDir)

```


```{r formatTcDataStructures}
source("functions/format_numeric_cols.R")
source("functions/format_tables.R")

term_labels <- c(
  "(Intercept)"      = "int",
  "rank_trial"       = "trial",
  "reward_sideRight" = "sideR",
  "sideAlt_trialTRUE" = "sideAltT"
)

formattingTablesDir <- "scripts/glm_analysis/formatting_tables/tc"
sourceFmt <- function(file) source(file.path(formattingTablesDir, file))

sourceFmt("format_emmTcPts.R") # outputs inLine and MsTab objects
sourceFmt("format_contTcLn.R") # outputs inLine and MsTab objects

contTcRsp # add this to list of tables? !!!! NULL output???

sourceFmt("format_mTcTidy.R") # outputs inLine and MsTab objects

tcRes <- list(
  mCoefsInLine = mTcTidyWideInLine,
  mCoefsMsTab = mTcCoefsMsTab,
  contrastsInLine = contTcLnInLine,
  contrastsMsTab = contTcLnMsTab,
  emmPtsInLine = emmTcPtsInLine,
  emmPtsMsTab = emmTcPtsMsTab,
  emmAll = emmTcAll,
  emmPts = emmTcPts,
  trialSlopeInLine = tcTrialSlopeInLine,
  trialSlopeMsTab = tcTrialSlopeMsTab
)

rm(
  mTc, mTcTidy, mTcTidyInLine, mTcTidyWideInLine,
  tcTrialSlopeInLine, tcTrialSlopeMsTab, mTcCoefsMsTab,
  emmTcAll, emmTcPts, emmTcPtsInLine,
  contTcLn, contTcLnInLine, contTcLnMsTab, contTcRsp,
  term_labels
)

rm(sourceFmt, formattingTablesDir)

```

```{r draftPubTables}

# create pub-ready tables?
 # # %>% separate this bit into a 'pub ready' table?
 #  select(c(experiment, rank_trial_middle, probConfint_middle,
 #           rank_trial_end, probConfint_end)) %>%
 #  arrange(experiment) %>%
 #  # rename it so it's publication-ready? or ready to go into paper?
 #  # (this will make indexing challenging)
 #  rename(
 #    `Pmiddle (95% CI)` = probConfint_middle,
 #    `Pend (95% CI)`    = probConfint_end,
 #    `Middle trial #`     = rank_trial_middle,
 #    `End trial #`        = rank_trial_end
 #  )

```

```{r buildRollingChoices}
# create a rolling-mean dataframe so underlying raw-data can be visualised
choices_rolling <- choices %>%
  arrange(rank_trial) %>%
  # keep nat or art along for the ride for easy subsetting later
  group_by(individual, experiment, nat_or_art, manipulation) %>%
  mutate(
    pcorr = rollmean(decision, k = 3, fill = NA, align = "center")
  ) %>%
  # average across individuals
  ungroup() %>% 
  group_by(rank_trial, experiment, nat_or_art, manipulation) %>%
  summarise(pcorr = mean(pcorr))

```

# Question 1: Can wasps use dorsal patterns?
    -   Looking at test versus control proportion correct
    -   Slope in test and control
    -   EMmeans at end of test and control
        -   is this essentially equivalent to binning the last n trials and making the comparison?

```{r q1PlotAndFilterTables}

q1ID <- "perpPara_170725"
# this function allows you to subset not just by columns but also rownames
tcResQ1 <- lapply(tcRes, function(x) {
  if ("experiment" %in% colnames(x)) {
    dplyr::filter(x, experiment == q1ID)
  } else if (q1ID %in% rownames(x)) {
    x[q1ID, , drop = FALSE]
  } else {
    x
  }
})
mCoefsInLineQ1 <- tcResQ1$mCoefsInLine
contrastsInLineQ1 <- tcResQ1$contrastsInLine
emmTcPtsInLineQ1 <- tcResQ1$emmPtsInLine
emmPtsQ1 <- tcResQ1$emmPts
emmAllQ1 <- tcResQ1$emmAll

df_rolling <- choices_rolling %>% filter(experiment == q1ID)

p <- ggplot(data = emmAllQ1, aes(x = rank_trial))+
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL), alpha = 0.2) +
  geom_line(aes(x = rank_trial, y = prob)) +
  labs(x = "Trial", y = "% of decisions for reward")+
  scale_y_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.1))+
  geom_hline(yintercept = 0.5, lty = 2)+
  plotStyle$themeTextEnlarged+
  facet_wrap(vars(manipulation))

p <- p +
    geom_errorbar(data = emmPtsQ1,
                aes(x = rank_trial , ymin = asymp.LCL, ymax = asymp.UCL),
                width= 2) +
  geom_point(data = emmPtsQ1, aes(x = rank_trial, y = prob))

p + geom_point(data = df_rolling, aes(x = rank_trial, y = pcorr),
               colour = "grey")
emmTcPtsInLineQ1$confintFmt_testEnd
contrastsInLineQ1
```

During the test phase of the experiment, trial number (experience) had a significant positive effect on the expected probability (\Pcorr) of a correct decision (Figure 1 solid line) with every successive trial increasing the log odds of a correct decision by `r mCoefsInLineQ1$trial_est` (95% CI `r mCoefsInLineQ1$trial_confint`, p `r mCoefsInLineQ1$trial_pFmt`).

The \Pcorr of a correct choice at the end of the test was higher (\Pcorr = `r emmTcPtsInLineQ1$probFmt_testEnd`, 95% CI `r emmTcPtsInLineQ1$confintFmt_testEnd`) than at the start of the control (\Pcorr = `r emmTcPtsInLineQ1$probFmt_ctrlStart`, 95% CI: `r emmTcPtsInLineQ1$confintFmt_ctrlStart`), and this difference was significant (log odds ratio = `r contrastsInLineQ1$logOddsRatio`, p `r contrastsInLineQ1$pFmt`) (Figure 1, compare error bars between test and control panel).

Also note that \Pcorr is significantly above chance (95% confidence ribbon does not overlap the 50% line) from an early trial number and remains that way until the end of the test. In contrast, the \Pcorr in the control phase is never significantly above chance for the duration of the control (95% confidence ribbon overlaps the 50% line).

That the model suggests naive wasps perform above chance at the onset of the test phase (ie. in trial 1) can be attributed to the fact that the model is unable to fit the rapid learning of the wasps, rather than to the availability and learning of olfactory and / or temporal cues during the pre-test training phase. This is supported by the proportion of correct decisions in the first few 3-trial wide windows of the test phase (black points) that are clustered around 50%.

```{r q1Cleanup}
rm(
  q1ID, tcResQ1, mCoefsInLineQ1, contrastsInLineQ1,
  emmTcPtsInLineQ1, emmPtsQ1, emmAllQ1,
  df_rolling, p
)
```

# Question 2: What information are wasps using to discriminate patterns? 
- Do they need optic flow? 
- Can they distinguish simple brightness differences? 
- are there differences in performance among artificial stimuli?

```{r q2FromMaster}

emmArtAll <- testRes$emmAll %>%
  filter(nat_or_art == "artificial")

p <- ggplot(emmArtAll, aes(x = rank_trial, y = prob)) +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL), alpha = 0.2) +
  geom_line() +
  labs(x = "Trial", y = "% of decisions for reward") +
  scale_y_continuous(labels = scales::percent) +
  geom_hline(yintercept = 0.5, lty = 2) +
  plotStyle$themeTextEnlarged +
  facet_wrap(vars(experiment))

# add binned points from master rolling object
df_rolling <- choices_rolling %>%
  filter(manipulation == "test", nat_or_art == "artificial")

p + geom_point(data = df_rolling, aes(x = rank_trial, y = pcorr),
               colour = "grey")

# table used in Q2 inline writing (from master display table)
emmArt <- testRes$emmPtsInLine %>%
  tibble::rownames_to_column("experiment") %>%
  filter(nat_or_art == "artificial") %>%
  tibble::column_to_rownames("experiment")

#

```


```{r q2ContrastArtStimuli}
# Option 2: one-row-per-experiment trial-slope table for Q2
q2TrialSlopeTable <- testRes$trialSlopeInLine %>%
  filter(nat_or_art == "artificial") %>%
  select(-nat_or_art)

formatSlopeTable(
  q2TrialSlopeTable,
  caption = "Q2 trial-slope summary by artificial experiment"
)


```

To answer whether wasps require optic flow information to discriminate patterns we tested whether they could distinguish between oblique stripes oriented at 45 degrees to the right or left of the y-maze arm's long axis and the general direction of wasp travel. 

Wasps had no trouble distinguishing between oblique stripes that presumably produce identical rates of optic flow in the dorsal visual field (Figure 2). Similar to the perpendicular-parallel experiment, trial had a significant positive effect on \Pcorr, with every successive trial increasing the log odds of a correct decision by `r q2TrialSlopeTable["thinOb_150823", "trialLogOdds"]` (95% CI `r q2TrialSlopeTable["thinOb_150823", "ci95"]`, p `r q2TrialSlopeTable["thinOb_150823", "pFmt"]`; Table 1). Initially (at trial 1) performance was not significantly different from chance (\Pcorr = `r emmArt["thinOb_150823", "first_probFmt"]`, 95% CI: `r emmArt["thinOb_150823", "first_confintFmt"]`) but rose steeply, reaching `r emmArt["thinOb_150823", "last_probFmt"]` (95% CI: `r emmArt["thinOb_150823", "last_confintFmt"]`) by the end of the experiment (trial 66), which is significantly higher than expected by chance (50%).

Next, we asked whether wasps could discriminate between an opaque and transparent roof, ie. between stimuli that carried little to no pattern information. While trial had a positive effect on \Pcorr (beta = `r q2TrialSlopeTable["brightDiff_250725", "trialLogOdds"]`, 95% CI `r q2TrialSlopeTable["brightDiff_250725", "ci95"]`), unlike for the other two pairs of artificial stimuli this effect was not significant (p = `r q2TrialSlopeTable["brightDiff_250725", "pFmt"]`), likely due to the much shorter number of trials this experiment was run for. While statistical support for a positive slope is lacking, there is support for \Pcorr > 50% towards the middle and end of the experiment. At the onset of the experiment (trial 1), wasp performance was not significantly different from 50% (\Pcorr = `r emmArt["brightDiff_250725", "first_probFmt"]`, 95% CI: `r emmArt["brightDiff_250725", "first_confintFmt"]`))  but rises with experience and by the end of the experiment (trial 26) \Pcorr reached `r emmArt["brightDiff_250725", "last_probFmt"]` (95% CI: `r emmArt["brightDiff_250725", "last_confintFmt"]`). Performance at the end of the experiment is only borderline significantly higher than 50% because of the increased uncertainty in the slope / effect of trials on performance due to the lower number of trials run in this experiment. However, if one uses other metrics or analyses to compare performance to the 50% line, they are significantly different (for example, comparing performance at an intermediate trial or comparing the average performance of the last five trials to the 50% line).

NBNB! Slope or brightdiff exp not significant. fade best fit line?

Comparison among different artificial stimuli:

issues: - day is mulitcollinear in thin oblique experiment. It makes the slope of thin oblique appear less steep. This drives the difference in slopes detected between perppara and thin oblique. The issue is, is it real? I'm not confident enough that I ran the experiments in exactly the same way so as to make them comparable. If we remove day from the analysis, would we still find a significant difference in the slopes? Could the difference simply be attributable to slower learning due to the side bias which is clearly evident in the thin oblique experiment (possibly caused because of different pre-testing training regimes). Why even is there a side bias when these wasps had just come off the back of a previous experiment with a thick oblique stripe? was the side bias present at that time? - the issue im trying to get at above is that conclusions regarding slope diffs depend on the model you run. - massive confidence intervals around brightness experiment

# Question 3: Can wasps use naturalistic patterns for navigation? 
- Are performances different from 50%?
- Are performances different from the control?
- Are there differences in performance between naturalistic and artificial stimuli?

```{r q3NaturalisticTest}
#| fig-width: 4
#| fig-height: 8

emmNatTestAll <- testRes$emmAll %>% filter(nat_or_art == "naturalistic")
emmNatTestPtsLong <- testRes$emmPts %>% filter(nat_or_art == "naturalistic")
emmNatTestPts <- testRes$emmPtsInLine %>% filter(nat_or_art == "naturalistic")

# use master rolling object
df_rolling <- choices_rolling %>%
  filter(manipulation == "test", nat_or_art == "naturalistic")

ggplot(emmNatTestAll, 
            aes(x = rank_trial, y = prob)) +
  geom_point(data = df_rolling, aes(x = rank_trial, y = pcorr),
               colour = "grey") +
  geom_line() +
  geom_ribbon(
    aes(ymin = asymp.LCL, ymax = asymp.UCL),
    alpha = 0.15,
    colour = NA
  ) +
  ylim(0, 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  facet_wrap(vars(experiment), ncol =2)+
  ylab("P(correct)")+
  theme_bw()+ 
  theme(legend.position = "none")


```

```{r q3TablePts}
# table with pcorr at start and end of experiment (plus last trial number)
q3NatTestPtsTable <- testRes$emmPtsMsTab %>%
  # could save on a lot of lines / repetition if nat_or_art always comes along
  left_join(
    unique(choices[, c("experiment", "nat_or_art")]),
    by = "experiment"
  ) %>%
  filter(nat_or_art == "naturalistic") %>%
  select(-c(middleTrial, testMidPcorr95CI))

knitr::kable(
  q3NatTestPtsTable,
  caption = "Naturalistic test performance at first and last trial",
  booktabs = TRUE
)

```

Evidence for whether wasps can discriminate naturalistic canopies at above-chance rates (>50%) is mixed. In four of the seven naturalistic canopy pairs we tested, the predicted \Pcorr by the end of the experiment was significantly above chance (the lower limit of the 95% CI is > 50%, see Table x), suggesting wasps may be able to separate certain pairs of naturalistic canopies to some degree (assuming no other information was available to the wasps). 

```{r q3NaturalisticTestControl}

# control comparison: compare the control to the test
# bring in the predictions across all trials and the subset for end of test and start of control
emmNatTcAll <- tcRes$emmAll %>% filter(nat_or_art == "naturalistic")
emmNatTcPts <- tcRes$emmPts %>% filter(nat_or_art == "naturalistic")
tbNatTcPts <- tcRes$emmPtsInLine %>% filter(nat_or_art == "naturalistic")

## is this whole section below necessary?? 
# below line just checks which naturalistic experiments have a test and control
expTestAndCtrl <- names(
  which(
    tapply(choices$manipulation, choices$experiment,
           function(x) length(unique(x)) > 1)))

choicesRollTc <- choices_rolling %>%
  filter(nat_or_art == "naturalistic" & experiment %in% expTestAndCtrl) 

# add the best fit line and CIs to plots
p <- ggplot(emmNatTcAll, aes(x = rank_trial, y = prob, colour = experiment)) +
  geom_line() + 
  geom_ribbon(
    aes(ymin = asymp.LCL, ymax = asymp.UCL, fill = experiment),
    alpha = 0.15,
    colour = NA
  ) +
  ylim(0, 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  facet_grid(experiment ~ manipulation)+
  ylab("P(correct)")+
  theme_grey()+ 
  theme(legend.position = "none")

p + 
  geom_point(data = choicesRollTc, aes(x = rank_trial, y = pcorr))+
  geom_hline(yintercept = 0.5, linetype = "dashed")+
  facet_grid(experiment ~ manipulation, space = "free", scales = "free_x")

p <- ggplot(emmNatTcPts, aes(x = manipulation, y = prob,
                               ymin = asymp.LCL, ymax = asymp.UCL)) +
  geom_point() +
  geom_errorbar(aes()) +
  ylim(0, 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  facet_wrap(vars(experiment), scales = "free")+
  ylab("P(correct)")+
  theme(legend.position = "none")

# can compare the average of the n control trials to the average of the last n test trials 
# could look at wasps present / days / other variables to 
# make sure they're somewhat equal between the comparisons

```

```{r q3TableTcPts}
q3NatTcPtsTable <- tcRes$emmPtsMsTab %>%
  left_join(
    unique(choices[, c("experiment", "nat_or_art")]),
    by = "experiment"
  ) %>%
  filter(nat_or_art == "naturalistic") %>%
  select(
    experiment,
    testEndPcorr95CI,
    controlStartPcorr95CI,
    testEndTrial
  )

knitr::kable(
  q3NatTcPtsTable,
  caption = "Naturalistic test-control performance at test end and control start",
  booktabs = TRUE
)

```

naturalistic test vs control

nat vs art:
Discrimination performance for naturalistic canopies tends to be lower than for artificial canopies (make some sort of comparison or just give ranges) and 






Produce necessary tables to report from in-line and to include in MS. 

Write results here:
Evidence that wasps can discriminate naturalistic canopies from the test vs control analysis is also mixed. 

Coming soon: 1. comparison of naturalistic stimuli versus artificial

ToDo:
- make master tables
- add end-trial estimates and CIs to all figures (q2 and q3 outstanding)
- x and y figure axis labels
- table headers and rownames need to be formatted for pub. 
- pub-ready experiment names?
  - eg. perpendicular / parallel and oblique (+45 - 45)
- diffuser exp data in supplementary
- naturalistic -> artificial transition experiment 

# Supplementary  
```{r}
testRes$emmPtsMsTab


```
